PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
added phq 8 item cut off chunks

@@

@@

>>>>

```{r PHQ baseline missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.base_cut_off = 
      if_else(
        na_per_person_phq_base == 1 & 
          is.na(phq.dead_hurting_thoughts_base_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
```

@@

```{r PHQ retro missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.retro_cut_off = 
      if_else(
        na_per_person_phq_retro == 1 & 
          is.na(phq.dead_hurting_thoughts_retro_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
```

@@

```{r PHQ prepan missingness 8 items}
#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.prepan_cut_off = 
      if_else(
        na_per_person_phq_prepan == 1 & 
          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
        1,
        0
      )
  )

table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
```
